---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Boxplot

The Boxplot package has been designed to allow users to create aestheticly pleasing and clean-looking boxplots. This package has specifically been designed for plotting numerical data across a variety of different categories. This package contains 1 function, the boxplot_numeric_category function, which plots a numeric variable across the categories of a categorical variable. This function also cleans the dataset before creating the boxplot by removing any NA values from the dataset. This function works for a variety of different datasets, as can be seen in the examples section of the documentation for the boxplot_numeric_category function, and in the examples section below.

## Installation

You can install the development version of Boxplot from [GitHub](https://github.com/) with:

``` 
# install.packages("devtools")
devtools::install_github("juliafast/Boxplot")
```

## Examples

*For the below examples, I will be using some of the datasets contained in the r `datasets` and `dplyr` packages. I will also use piping, which requires the `magrittr` package. These packages will have been installed as part of downloading the Boxplot package* 

```{r}
#load the Boxplot, datasets, dplyr, and magrittr packages to execute the below examples
library(Boxplot)
library(datasets)
library(magrittr)
library(dplyr)
```

### Example 1

Below is a basic example which shows you how to use the boxplot_numeric_category function.

The boxplot_numeric_category function in the `Boxplot` package can be used to create a boxplot from data contained in the "CO2" dataframe from the r `datasets` package that shows the distribution of CO2 concentration of grass plants in each of two treatment types (chilled or nonchilled):
```{r example}

#create a boxplot showing the distribution of CO2 concentration across each treatment type
boxplot_numeric_category(dataframe = CO2, x = Treatment, y = conc)

```

### Example 2

Below is an example which shows you how to use the boxplot_numeric_category function while using piping to keep the code clean.

The boxplot_numeric_category function can be used to create a boxplot from data contained in the "starwars" dataset from the `dplyr` package that shows the distribution of the height of starwars characters based on the sex of the characters:
```{r}

#create a boxplot showing the distribution of height of starwars characters based on the sex of the characters
starwars %>% boxplot_numeric_category(sex, height)

```

### Example 3

Below is an example which shows you how to use the boxplot_numeric_category function in conjunction with another function, in this case the **filter** function from the `dplyr` package.

The boxplot_numeric_category function can be used to create a boxplot from data contained in the "storms" dataset from the `dplyr` package that shows the distribution of the wind speeds observed for each of the storms Caroline and Doris:

```{r}

#filter the name column of the storms package to only include the "Amy" and "Doris" storm names
#create a boxplot showing the distribution of wind speeds observed for the two storms "Amy" and "Doris"
boxplot_numeric_category((storms %>% filter(name == c("Amy", "Doris"))), name, wind)

```

## References for Function Code

Elferts D. 2016. Remove all of x axis labels in ggplot [duplicate]. Stack Overflow; [modified 2016 Jan 29; accessed 2021 Oct 25]. https://stackoverflow.com/questions/35090883/remove-all-of-x-axis-labels-in-ggplot

Leon. 2020. Removing NA from used column in ggplot. R Studio Community; [modified 2020 Aug 16; accessed 2021 Nov 2]. https://community.rstudio.com/t/removing-na-from-used-column-in-ggplot/76579
