---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Boxplot

The Boxplot package has been designed to allow users to create aestheticly pleasing and clean-looking boxplots. This package has specifically been designed for plotting numerical data across a variety of different categories. This package contains 1 function, the boxplot_numeric_category function, which plots a numeric variable across the categories of a categorical variable. This function also cleans the dataset before creating the boxplot by removing any NA values from the dataset. This function works for a variety of different datasets, as can be seen in the examples section of the documentation for the boxplot_numeric_category function, and in the examples section below.

## Installation

You can install the development version of Boxplot from [GitHub](https://github.com/) with:

``` 
# install.packages("devtools")
devtools::install_github("juliafast/Boxplot")
```

## Examples

*For the below examples, I will be using some of the datasets contained in the r `datasets` and `dplyr` packages. I will also use piping, which requires the `magrittr` package. These packages will have been installed as part of downloading the Boxplot package* 

Below is a basic example which shows you how to use the boxplor_numeric_category function.

The boxplot_numeric_category function in the `Boxplot` package can be used to create a boxplot from data contained in the "CO2" dataframe from the r `datasets` package that shows the distribution of CO2 concentration of grass plants in each of two treatment types (chilled or nonchilled):
```{r example}
## load the Boxplot package
library(Boxplot)
library(datasets)

boxplot_numeric_category(dataframe = CO2, x = Treatment, y = conc)

```

Below is a basic example which shows you how to use the boxplor_numeric_category function while using piping to keep the code clean:

The boxplot_numeric_category function can also be used to create a boxplot from data contained in the "starwars" dataset from the `dplyr` package that shows the distribution of the height of starwars characters based on the sex of the characters:
```{r}
## load the Boxplot package and magrittr package 

library(magrittr)
library(dplyr)

starwars %>% boxplot_numeric_category(sex, height)
```

Below is an example which shows you how to use the boxplot_numeric_category function in conjunction with other functions, in this case the **filter** function from the `dplyr` package.

The boxplot_numeric_category function can also be used to create a boxplot from data contained in the "storms" dataset from the `dplyr` package that shows the distribution of the wind speeds observed for each of the storms Caroline and Doris:

```{r}

## load the Boxplot package and magrittr package


boxplot_numeric_category((storms %>% filter(name == c("Amy", "Doris"))), name, wind)

```

Below is an example which shows you how not to use the boxplot_numeric_category function. 

Below is a line of code that shows a use of the boxplot_numeric_category function that will return an error message. This function requires a categorical input for the "x" argument and a numeric input for the "y" argument. 

Using the "starwars" dataset from the dplyr package, we will attempt to use the boxplot_numeric_category function to create a boxplot that shows the distribution of the name of starwars characters based on the sex of the characters. Because the y input below, name, is not a numeric input, an error message will appear:

```{r, error=TRUE}

boxplot_numeric_category(starwars, sex, name)

```

